Compiling refinement types to dependent types

### 2020-07-06 tex/paper.tex
Ok, I completely forgot the correct way of doing theorems

\theorem For any well-typed surface language term $\nonterm{es}$, the result of the translation $\mu_\epsilon(\nonterm{es})$ is well-typed in the core language:
\[
  \nonterm G \vdash \nonterm{es} : \nonterm{ts} \implies \mu_\Gamma(\nonterm G) \vdash \mu_\epsilon(\nonterm{es}) : \mu_\tau(\nonterm{ts})
\]

>>>>

\begin{theorem}
  For any well-typed surface language term $\nonterm{es}$,
  the result of the translation $\mu_\epsilon(\nonterm{es})$ is well-typed in the core language:
  \[
    \nonterm G \vdash \nonterm{es} : \nonterm{ts} \implies \mu_\Gamma(\nonterm G) \vdash \mu_\epsilon(\nonterm{es}) : \mu_\tau(\nonterm{ts})
  \]
\end{theorem}
